A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-03-15 paper/paper.tex
starting to update paper

\author{Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and P. Arbenz\footnotemark[4]
}

@@

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{PSI, Villigen, Switzerland}
\footnotetext[3]{IBM Research -- Zurich, Switzerland}
\footnotetext[4]{Department of Computer Science, ETH Zurich, Switzerland}
\footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
\footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
\renewcommand{\thefootnote}{\arabic{footnote}}

@@

The next section introduces the notation of multi-objective optimization
  theory and describes the first implemented optimizer.
In Section~\ref{sec:framework} we discuss the implementation of the framework.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application of a beam dynamics problem is
  discussed in Section~\ref{sec:experiments}.

@@

The authors thank the \textsc{SwissFEL} team for contributing to the
  formulation of optimization problems.

\appendix

>>>>

\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and P. Arbenz\footnotemark[4]
}

@@

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{PSI, Villigen, Switzerland}
\footnotetext[3]{IBM Research -- Zurich, Switzerland}
\footnotetext[4]{Department of Computer Science, ETH Zurich, Switzerland}
\footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
\footnotetext[1]{Illinois Institute of Technology, Chicago, USA}
\footnotetext[8]{Argonne National Laboratory, Lemont, USA}
\footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
\renewcommand{\thefootnote}{\arabic{footnote}}

@@

The next section introduces the notation of multi-objective optimization
  theory and describes the first implemented optimizer.
In Section~\ref{sec:framework} we discuss the implementation of the framework.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application in two beam dynamics problems is
  discussed in Section~\ref{sec:experiments}.

@@

The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
  formulation of optimization problems. We gratefully acknowledge the computing resources provided on Bebop, a high-performance computing cluster operated by the Laboratory Computing Resource Center at Argonne National Laboratory.
\appendix

### 2018-03-15 paper/theor-experiment.tex
starting to update paper

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
    rmsx:  OBJECTIVE, EXPR="fromFile("rms_x-err.dat", "var")";
    emitx: OBJECTIVE, EXPR="fromFile("emit_x-err.dat", "var")";
    match: OBJECTIVE, EXPR="fabs(fromFile("emit_x-peak.dat", "var") -
                                 fromFile("rms_x-peak.dat", "var"))";
\end{verbatim}}
\vspace{0.2cm}

@@

\subsection{Optimization Results}

@@

>>>>

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
    rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
    emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
    match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
                                 statVariableAt("rms_x-peak.dat", "var"))";
\end{verbatim}}
\vspace{0.2cm}

@@

\subsubsection{Optimization Results}

@@

\subsection{AWA}
Next we apply the optimization framework to an ongoing project in accelerator physics.
The model is taken from the Argonne Wakefield Accelerator facility, which 
houses two rf photoinjector beam lines. We consider the high charge beam line
that consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
and

\subsubsection{AWA Optimization Results}
